Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-18 draft.Rmd
Update draft.Rmd

We our approach is a parallel case study  which uses two longitudinal panels, the British Household Pnael Survey, and the German Socio-Economic Panel. It has three strengths. First, we include firm internal mobility into our analysis of mobility types. Second, take a longitudinal approach to estimating the effects of changing jobs. In this way, we avoid the conclusions of authors who compare movers to non-movers; instead we are able to observe the effects of moving from one position to another. Third, we compare and contrast the effects of moving in two different institutional settings, where authors typically rely on one.

We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary" mobility types. Internal promotions yield higher pay for workers in both countries. Quits have a minor effect, which are largely explained by changes in working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany. This high premium may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The minor effect of internal promotions in the UK, means workers must be able to pursue several promotions before seeing a substantial change in pay.

The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). The narrative suggests that workers are able to gain through quits what was on offer through promotion. Our findings suggest that promotion and quits are distinctly different mechanisms for improving earnings. Further countries with limited mobility between firms, also have high rewards tied to internal mobility.

The article is structured as follows; section one summarises the theoretical literature on job mobility and earnings. Section two considers the theretical literature on country differences in labour market institutions. Section three outlines empirical findings and introduces our hypothesis. Section four summarises our methodology. Section five lists the results, and a brief cdiscussion cloncudes the article.

## Micro-level theories on mobility

What are the micro-level theories on mobility and outcomes?

@@

## Macro-level theories on mobility

## Institutional differences

### Data and sample:

>>>>

Our approach is a parallel case study using two longitudinal panels, the British Household Panel Survey, and the German Socio-Economic Panel. It has three strengths. First, we include internal mobility (promotions) in our analysis, which is often ignored. Second, we take a longitudinal approach to estimating the effects of changing jobs. In this way, we avoid the conclusions of authors who compare movers to non-movers; instead we are able to observe the effects of moving from one position to another. Third, we compare and contrast the effects of moving in two different institutional settings, where authors typically rely on one. This approach allows us to compare and contrast the importance of local institutions on job mobility.

We offer two findings. First, quits and promotions have significantly different effects on earnings growth. Quits have a minor effect, which disappears when controlling for changes in working hours. Promotions have a significant positive effect in both countries which remains even when controlling for industry and occupational mobility (the effect is "pure", as argued by Tahlin etc). Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany. This high premium may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The minor effect of internal promotions in the UK, means workers must be pursue several promotions before seeing a substantial change in pay.

The article helps to understand processes of inequality, where workers best placed to pursue promotion, are those most likely to see higher earnings later in their career. The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). The narrative suggests that workers are able to gain through quits what was on offer through promotion. Our findings suggest that promotion and quits are distinctly different mechanisms for improving earnings. Although mobility ay be a necessary strategy to place oneself near an internal career lader, access to promotions may be understood as an important key to understanding inequality in both countries.

The article is structured as follows; section one summarises the theoretical literature on job mobility and earnings. Section two considers the theretical literature on country differences in labour market institutions. Section three outlines empirical findings and introduces our hypothesis. Section four summarises our methodology. Section five lists the results; a brief discussion concludes the article.

@@

## Mobilities, earnings, and institutions

## Data and sample:
